\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{textcomp}

% Colors
\definecolor{accent}{HTML}{2BB673}

% Hyperlink styling
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

% Section formatting
\titleformat{\section}
  {\color{accent}\Large\bfseries}
  {}{0pt}{}[\vspace{-6pt}\color{accent}\rule{\linewidth}{1.2pt}]
\titlespacing*{\section}{0pt}{12pt}{6pt}

\titleformat{\subsection}
  {\normalsize\bfseries}
  {}{0pt}{}
\titlespacing*{\subsection}{0pt}{6pt}{2pt}

% Bullet list spacing
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, topsep=2pt, parsep=0pt}
\renewcommand{\labelitemi}{-}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% ---------- HEADER ----------
{\fontsize{26}{30}\selectfont Kaushik R Bangera}\\[2pt]
{\color{accent}\large Senior Backend Engineer \textbar{} Distributed Systems \textbar{} Real-Time Systems \textbar{} AWS}\\[2pt]
\href{mailto:kaushikrb909@gmail.com}{kaushikrb909@gmail.com} \textbar{} +91 9731176618\\
\href{https://kaushikrb.com/}{Portfolio} \textbar{} \href{https://github.com/NeuronEnix}{GitHub} \textbar{} \href{https://www.linkedin.com/in/kaushik-r-bangera/}{LinkedIn}

% ---------- SUMMARY ----------
\section*{SUMMARY}
Senior backend engineer with \textbf{4.5+ years} of experience building \textbf{high-scale}, \textbf{real-time} gaming systems and \textbf{cloud-native} infrastructure on \textbf{AWS}. Proven in scaling production traffic to \textbf{\textasciitilde{}600K requests/min}, designing fault-tolerant event pipelines, improving payments correctness, and driving reliability through \textbf{strong observability and incident ownership}. Strong in \textbf{system design}, \textbf{performance optimization}, and \textbf{execution leadership} in fast-paced environments.

% ---------- TECHNICAL SKILLS ----------
\section*{TECHNICAL SKILLS}
\textbf{Languages:} TypeScript, JavaScript, Python, SQL, Go\\
\textbf{Backend:} Node.js, REST APIs, WebSockets, gRPC, Microservices, Distributed Systems, System Design, Event-driven Systems, CDC (Logical Replication), ETL\\
\textbf{Databases:} PostgreSQL (RDS/Aurora), MySQL (Aurora), ClickHouse, MongoDB, Redis\\
\textbf{AWS:} Lambda, EC2, EKS, S3, API Gateway, Kinesis, Firehose, Step Functions, Glue, Athena, SQS, Cognito, CloudWatch, Amazon Personalize\\
\textbf{DevOps \& Tools:} Docker, Kubernetes, Terraform (IaC), NGINX, Git, Airflow, CI/CD, Datadog, Locust, Percona Monitoring, Tailscale

% ---------- EXPERIENCE ----------
\section*{EXPERIENCE}

\subsection*{{\color{accent}Jumbo --- New Delhi} \textnormal{-} Senior Backend Engineer (Founding Engineer)}
\textbf{Aug 2024 -- Present}
\begin{itemize}
  \item Scaled the gaming platform to \textbf{\textasciitilde{}600,000 requests/min}, reliably handling \textbf{INR 5 Cr peak payment} throughput and \textbf{30 Cr+ in-game transaction} volume.
  \item Rewrote the \textbf{core transaction service in Go + gRPC}, reducing latency to single-digit ms while ensuring financial correctness through \textbf{atomicity, idempotency, running balances}, and integer-based currency normalization to \textbf{eliminate float drift}; built with \textbf{TDD and spec-driven development}.
  \item Designed a \textbf{multi-currency wallet ledger} with \textbf{liability tracking} and automated \textbf{clawback reconciliation} for accurate, auditable balances across product lines.
  \item Built a \textbf{vendor-agnostic event pipeline}: services emit a single typed event that is batched, streamed through \textbf{Redis}, and \textbf{fanned out to multiple analytics vendors} (CleverTap, PostHog, OpenPanel, Matomo), with every event also persisted \textbf{first-party in ClickHouse} --- removing third-party lock-in and reducing new-vendor onboarding to a config change.
  \item Built a \textbf{CDC pipeline} using \textbf{Postgres logical replication} to stream production data into the analytics warehouse (\textbf{BigQuery}) in near real time, without loading the primary database.
  \item Owned the end-to-end \textbf{system architecture} for the in-house fantasy platform, defining \textbf{service boundaries, database schema, and API contracts} for scalable delivery.
  \item Built the \textbf{fantasy contest engine} --- concurrency-safe contest join, automated \textbf{reward calculation \& distribution}, live leaderboards, and refund/cancellation flows for abandoned or under-filled contests.
  \item \textbf{Reduced backend load and CDN/edge-serving cost by \textasciitilde{}40--50\%} by moving low-change/high-read APIs \textbf{behind a CDN} with correct \textbf{cache-control} headers --- cached at the \textbf{Cloudflare edge} and on-device.
  \item Delivered an async \textbf{recharge + KYC orchestration layer} using a vendor-agnostic \textbf{Adapter Pattern}, reducing third-party dependency cost by \textbf{\textasciitilde{}70\%} through caching and retries.
  \item Developed a scalable \textbf{WebSocket platform (API Gateway + Redis)} for connection state, channel broadcasts, and WebSocket-based API calls.
  \item Built centralized \textbf{logging + trace correlation} (ClickHouse + Redis) using \textbf{Node.js async\_hooks}, reducing MTTR and surfacing performance bottlenecks across services.
  \item Improved \textbf{tail latency} and peak resilience through \textbf{API + DB bottleneck} analysis and \textbf{load testing} using \textbf{Locust, Percona, and ClickHouse}.
  \item Rolled out \textbf{Datadog} observability (APM, metrics, dashboards, and alerting) across all production services, improving incident detection and response.
  \item Reclaimed \textbf{\textasciitilde{}50\% of database storage} using \textbf{pg\_repack} to rebuild bloated tables, reindex, and clear dead tuples, and upgraded \textbf{PostgreSQL to a new major version} --- improving cache efficiency and query performance.
  \item Scaled database reads using \textbf{read replicas, RDS Proxy, and pgBouncer} connection pooling, and tuned \textbf{autoscaling} to absorb peak traffic without saturating the primary.
  \item Modernized AWS infrastructure and security using \textbf{AWS Organizations, CI/CD pipelines, and IAM Identity Center RBAC}, securing internal access via \textbf{Tailscale} and enforcing least-privilege operations.
  \item Strengthened system integrity with \textbf{OTP abuse prevention} and \textbf{multi-device concurrency conflict handling} for account safety and reliability.
  \item Served as the \textbf{primary escalation owner} for production incidents, leading debugging, \textbf{incident resolution}, and release execution while unblocking the team.
  \item Built an \textbf{Aviator game} from scratch and scaled it to \textbf{\textasciitilde{}1,000 CCU}, improving engagement through stable gameplay loops and production hardening.
  \item Performed \textbf{zero-downtime rotation} of \textbf{JWT signing keys} (\texttt{kid}-based) across all production services, with \textbf{no forced user logout}.
  \item Improved engineering velocity by using \textbf{AI-assisted tooling} and \textbf{MCP database workflows} for faster debugging, system insights, and architecture validation.
\end{itemize}

\subsection*{{\color{accent}Juego Studios --- Mangalore} \textnormal{-} Software Engineer (Backend / Cloud)}
\textbf{Aug 2021 -- Jan 2024}
\begin{itemize}
  \item Built a resilient AWS ingestion platform using \textbf{Kinesis}, reducing projected infrastructure cost by \textbf{\textasciitilde{}66\%} while improving throughput and reliability.
  \item Delivered end-to-end analytics pipelines using \textbf{AWS Glue ETL (PySpark) + Glue Catalog + Athena}, converting raw data to columnar \textbf{Parquet} to cut storage and reduce query latency from \textbf{\textasciitilde{}7s $\rightarrow$ 1--2s}.
  \item Researched and prototyped a \textbf{recommendation system} using \textbf{Amazon Personalize} for content and game discovery.
  \item Improved database scalability using \textbf{Aurora MySQL tuning}, \textbf{SQL transactions}, indexing, and \textbf{Redis caching}, achieving \textbf{\textasciitilde{}1,000 CCU and 1,000 RPS}.
  \item Provisioned and maintained cloud infrastructure using \textbf{Terraform (IaC)}, enabling reproducible deployments and consistent environments.
  \item Deployed and managed \textbf{multiplayer game} servers on \textbf{Kubernetes}, integrating \textbf{Agones} as a PoC for dedicated server scaling.
  \item Engineered server-side \textbf{game-loop infrastructure} --- a room/bucket system handling idle and timed-out rooms --- with \textbf{match-filling bots} to sustain gameplay during low player counts.
  \item Implemented secure authentication including \textbf{M2M architecture}, JWT \textbf{access/refresh token flows}, and \textbf{AWS Cognito + Secrets Manager} with role-based permissions.
  \item Delivered backend game logic across multiple multiplayer titles (\textbf{Texas Hold'em Poker}, \textbf{Rummy}, and an RPG with a quest/marketplace system), including matchmaking and concurrency-safe state.
  \item Built internal cost-optimization tooling including \textbf{Lambda memory benchmarking} and replacing \textbf{NAT Gateway with EC2 NAT}, reducing recurring AWS cost.
  \item Integrated secure wallet authentication flows using \textbf{Metamask} and \textbf{Keplr} for Web3 gaming features.
  \item Mentored engineers and collaborated across gameplay, frontend, CMS, and game design teams.
\end{itemize}

% ---------- EDUCATION ----------
\section*{EDUCATION}
\textbf{Srinivas Institute of Technology, Mangalore}\\
B.E. Computer Science Engineering (2021)

\end{document}
